---
title: "2nd week assignment"
author: "Simon Merino"
date: "5 de noviembre de 2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Airports, Ports and Train Stations Location, November 5th 2017, by Simon Merino

This webpage has been compiled for the 2nd week assignment of the Developing Data Products course.

It uses information downloaded from https://openflights.org/data.html to create a map that renders Airports, Ports and Train Stations locations accross the world.

The map is implemented to configure what kind of facilities users want to see as well as a double layer, one with OSM rendering and the other with a satellite view.

```{r libraries, echo=FALSE, warning = FALSE}
library(shiny)
library(leaflet)

```



```{r application, echo=FALSE}
shinyApp(
  
  ui = fluidPage(
  
  # Application title
  titlePanel("Airports, Ports and Train Stations Location, November 5th 2017"),
  
  # Sidebar with a slider input for number of bins 
  verticalLayout(

    
    # Show a plot of the generated distribution
       leafletOutput("map")

  )
),
  
  server = function(input, output) {
   
  output$map <- renderLeaflet({#Draw in a map location about Airports, Ports and Train Stations accross the world
    
    #Download the info
    url<-"https://raw.githubusercontent.com/jpatokal/openflights/master/data/airports-extended.dat"
    download.file(url,"airportsandmore.csv")
    
    #Create a proper dataframe
    airportsandmore<-read.csv("airportsandmore.csv",header=FALSE)
    columnNames<-c("Airport ID",
                   "Name",
                   "City",
                   "Country",
                   "IATA",
                   "ICAO",
                   "Latitude",
                   "Longitude",
                   "Altitude",
                   "Timezone",
                   "DST",
                   "Tz database time zone",
                   "Type",
                   "Source")
    
    #adding column names 
    #source: https://openflights.org/data.html
    
    colnames(airportsandmore)[] <- columnNames
    
    #dropping records whose type=="unknown"
    
    airportsandmore<-subset(airportsandmore,!Type=="unknown")
    
    #rename data column names
    colnames(airportsandmore)[which(names(airportsandmore) == "Latitude")] <- "lat"
    colnames(airportsandmore)[which(names(airportsandmore) == "Longitude")] <- "lng"
    
    
    
    
    # GRAPHICAL PART
    
    #Generate Icons
    airportIconUrl="http://en.wikipilipinas.org/images/archive/3/3f/20070629015340%21Airport_symbol.png"
    airportIcon<- makeIcon(iconUrl=airportIconUrl,iconWidth = 30,iconHeight=30)
    
    portIconUrl="https://upload.wikimedia.org/wikipedia/commons/thumb/8/81/Ship.svg/600px-Ship.svg.png"
    portIcon<- makeIcon(iconUrl=portIconUrl,iconWidth = 30,iconHeight=30)
    
    stationIconUrl="https://upload.wikimedia.org/wikipedia/commons/thumb/4/4b/Q55488_noun_19262_ccPierreLucAuclair_train-station.svg/2000px-Q55488_noun_19262_ccPierreLucAuclair_train-station.svg.png"
    stationIcon<-makeIcon(iconUrl=stationIconUrl,iconWidth = 30,iconHeight=30)
    
    
    # Select of lat and long columns
    airportsLocation<-airportsandmore[,7:8]
    
    #Create BaseMap
    
    map<-airportsLocation %>% 
      leaflet() %>% 
      addTiles(group="OpenStreetMap") %>%
      addProviderTiles('Esri.WorldImagery',group="SatelliteView") 
    
    #Add just airports  
    map<-map %>% 
      addMarkers(,lng=airportsLocation$lng[airportsandmore$Type=="airport"],lat=airportsLocation$lat[airportsandmore$Type=="airport"],icon=airportIcon, clusterOptions=markerClusterOptions(), popup =airportsandmore$Name[airportsandmore$Type=="airport"],group="Airports")
    
    
    #Add just ports  
    map<-map %>% 
      addMarkers(,lng=airportsLocation$lng[airportsandmore$Type=="port"],lat=airportsLocation$lat[airportsandmore$Type=="port"],icon=portIcon, clusterOptions=markerClusterOptions(), popup =airportsandmore$Name[airportsandmore$Type=="port"], group="Ports")
    
    #Add just stations 
    map<-map %>% 
      addMarkers(,lng=airportsLocation$lng[airportsandmore$Type=="station"],lat=airportsLocation$lat[airportsandmore$Type=="station"],icon=stationIcon, clusterOptions=markerClusterOptions(), popup =airportsandmore$Name[airportsandmore$Type=="station"], group="Train Stations")
    
    #Add control layer
    
    
    map<-map %>%
      addLayersControl(
        baseGroups = c("OpenStreetMap", "SatelliteView"),
        overlayGroups = c("Airports","Ports", "Train Stations"),
        options = layersControlOptions(collapsed = FALSE)
      )
    

  })
  

    
  },
  
  options = list(height = 500)
)
```



